An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-10-30 VLDB2026/main.tex
ok

\usepackage{array}
%\usepackage[all]{nowidow}
\usepackage{times}

@@

\begin{figure*}
	\centering
	\begin{minipage}[t]{0.37\textwidth}
		\centering
		\setlength{\abovecaptionskip}{-0.2cm}
		\setlength{\belowcaptionskip}{-0.3cm}
		\caption{Multi-Modal Datasets (RF)}
		\label{fig:range-multimodal} 
	\end{minipage}%
	\hfill
	\begin{minipage}[t]{0.27\textwidth}
		\centering
		\setlength{\abovecaptionskip}{-0.2cm}
		\setlength{\belowcaptionskip}{-0.3cm}
		\caption{Large-Scale Dataset (RF)}
		\label{fig: range big dataset}
	\end{minipage}
	\hfill % 在盒子之间添加弹性间距
	\begin{minipage}[t]{0.35\textwidth}
		\centering
		\setlength{\abovecaptionskip}{-0.2cm}
		\setlength{\belowcaptionskip}{-0.3cm}
		\caption{Different Platforms (RF)}
		\label{fig:range-cross-platform}
	\end{minipage}%

@@

	\textcolor{black}{In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions. }

		\textcolor{black}{
For example, in multi-attribute scenarios, some algorithms only support Boolean OR logic (e.g., FilterDiskANN), while others only support Boolean AND logic (e.g., NHQ and CAPS). Although algorithms such as ACORN, UNG, and Puck support both AND and OR logic across multiple attributes, they still struggle to handle complex Boolean expressions that involve nested combinations of conjunctions (AND) and disjunctions (OR). In contrast, while databases and the vector search library Faiss support more expressive Boolean logic, their performance is often suboptimal in queries involving only basic attribute filtering.
Therefore, designing algorithms that can support complex filtering expressions while maintaining high query efficiency remains a key challenge to be addressed. }

>>>>

\usepackage{array}
\usepackage[all]{nowidow}
\usepackage{times}

@@

\begin{figure*}
	\centering
	\begin{minipage}[t]{0.37\textwidth}
		\centering
		\setlength{\abovecaptionskip}{-0.2cm}
%		\setlength{\belowcaptionskip}{-0.15cm}
		\caption{Multi-Modal Datasets (RF)}
		\label{fig:range-multimodal} 
	\end{minipage}%
	\hfill
	\begin{minipage}[t]{0.27\textwidth}
		\centering
		\setlength{\abovecaptionskip}{-0.2cm}
%		\setlength{\belowcaptionskip}{-0.3cm}
		\caption{Large-Scale Dataset (RF)}
		\label{fig: range big dataset}
	\end{minipage}
	\hfill % 在盒子之间添加弹性间距
	\begin{minipage}[t]{0.35\textwidth}
		\centering
		\setlength{\abovecaptionskip}{-0.2cm}
%		\setlength{\belowcaptionskip}{-0.3cm}
		\caption{Different Platforms (RF)}
		\label{fig:range-cross-platform}
	\end{minipage}%

@@

In addition, existing attribute filtering algorithms face two major limitations: strict requirements on attribute format and limited support for complex filtering conditions. 
For example, in multi-attribute scenarios, some algorithms only support Boolean OR logic (e.g., FilterDiskANN), while others only support Boolean AND logic (e.g., NHQ and CAPS). Although algorithms such as ACORN, UNG, and Puck support both AND and OR logic across multiple attributes, they still struggle to handle complex Boolean expressions that involve nested combinations of conjunctions (AND) and disjunctions (OR). In contrast, while databases and the vector search library Faiss support more expressive Boolean logic, their performance is often suboptimal in queries involving only basic attribute filtering.
Therefore, designing algorithms that can support complex filtering expressions while maintaining high query efficiency remains a key challenge to be addressed.
